---
title: "Class Size"
author: "Lela Sengupta"
format: html
execute:
  echo: false
---

```{r}
#| label: setup
#| message: false
library(tidyverse)
library(brms)
library(tidybayes)
```

```{r}
#| message: false
class <- read_csv("STAR.csv")

class_1 <- class |>
  select(g4math, classtype, race) |>
  drop_na()
```

Question?
What is the causal effect of elementary school class size on current grade 4 math scores in the Southern US? 

Quantity of interest?
causal effect of class size on grade 4 math scores 

Preceptor Table 
units: individual elementary school students in the south
outcome: grade 4 math score 
covariates: class size, race, years in class type
treatment: causal model - class size 

population table: 
units: individual students in the US
source: 
time: 1970-2030
potential outcomes: math score for small class, math score for large class 
treatment: class size (small or large)
covariates: class size, race, years in class type

counterarguments for each: 
validity: 
Teachers may have inflated scores to make their classes look better. 

stability:
The test content and the school curriculum may have changed over time. 

representativeness: 
Because these scores are from Tennessee, they may not be reflective of all school districts within the southern US.

unconfoundedness: 
Certain districts may have received priority for small classes. 


